Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-09 doc/slides/hong+eisner.TLT13.slides.tex
slides so far
addressed some of Jason's minor comments

@@

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item[]  
    \item[]  
    \item[]  
  \end{itemize}
}

\section{Multi-headed}

\frame{\frametitle{Multi-headedness}
  \begin{itemize}
    \item Control
    \item Relativization
    \item Conjunction
  \end{itemize}
}

@@

%\frame{\frametitle{Multi-headedness}
%  \begin{figure}
%    \begin{dependency}
%      \begin{deptext}
%      I \& think \& the \& man \& who \& you \& saw \& wants \& to \& eat \& sushi \\
%      \end{deptext}
%      \deproot[edge above, thick]{2}{ROOT}
%      \depedge[edge above, thick, hide label]{2}{1}{} % think -> I
%      \depedge[edge above, thick, hide label]{4}{3}{} % man -> the
%      \depedge[edge above, thick, hide label]{4}{5}{} % man -> who
%      \depedge[edge above, thick, hide label]{7}{6}{} % saw -> you
%      \depedge[edge above, thick, hide label]{8}{4}{} % wants -> man
%      \depedge[edge above, thick, hide label]{4}{7}{} % man -> saw
%      \depedge[edge above, thick, hide label]{2}{8}{} % think -> wants
%      \depedge[edge above, thick, hide label]{8}{10}{} % wants -> eat
%      \depedge[edge above, thick, hide label]{10}{9}{} % eat -> to
%      \depedge[edge above, thick, hide label]{10}{11}{} % eat -> sushi
%      \depedge[edge below, edge style = {purple}, hide label, edge unit distance = 1.5ex, ultra thick]{10}{4}{} % eat -> man
%    \end{dependency}
%    \caption*{Example of a Multiheaded Parse}
%  \end{figure}
%}

@@

\frame{\frametitle{Link Grammars: Example Parse}
\begin{figure}
  \begin{dependency}[edge style={-}]
	\begin{deptext}
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	\depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	\depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	\depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	\depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	\deproot[edge above, thick, edge style = {red}]{2}{W}
	\deproot[edge above, thick, edge style = {red}]{7}{WV}
	\deproot[edge above, thick, edge style = {red}]{10}{X}
	\depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	\depedge[edge above, thick, edge style = {red}]{6}{5}{E}
  \end{dependency}
  \caption*{Link Parse of a sentence from Penn Tree Bank}
\end{figure}

@@

\frame{\frametitle{Link Grammars: Converting into a Directed Acyclic Graph}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	\depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	\depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	\depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	\depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	\deproot[edge above, thick, edge style = {red}]{2}{W}
	\deproot[edge above, thick, edge style = {red}]{7}{WV}
	\deproot[edge above, thick, edge style = {red}]{10}{X}
	\depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	\depedge[edge above, thick, edge style = {red}]{6}{5}{E}
  \end{dependency}

@@

\frame{\frametitle{Link Grammars}
Compare resulting dependency parse with CoNLL 2007 shared task. 
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\deproot[edge above, thick, edge style = {blue}]{3}{\small ROOT}
	\depedge[edge below, thick, edge style = {red}]{2}{3}{S}
	\depedge[edge above, thick, edge style = {blue}]{3}{2}{\small SBJ}
	\depedge[edge above, thick, edge style = {blue}]{3}{4}{\small ADV}
	\depedge[edge above, thick, edge style = {blue}]{3}{5}{\small ADV}
	\depedge[edge below, thick, edge style = {red}]{3}{6}{I}
	\depedge[edge above, thick, edge style = {blue}]{3}{6}{\small VC}
	\depedge[edge above, thick, edge style = {blue}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge below, thick, edge style = {red}]{2}{1}{D}
	\depedge[edge above, thick, edge style = {blue}]{2}{1}{\small NMOD}
	\depedge[edge below, thick, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, thick, edge style = {blue}]{7}{8}{\small ADV}
	\depedge[edge below, thick, edge style = {red}]{6}{7}{P}
	\depedge[edge above, thick, edge style = {blue}]{6}{7}{\small VC}
	\depedge[edge below, thick, edge style = {red}]{8}{9}{J}
	\depedge[edge above, thick, edge style = {blue}]{8}{9}{\small PMOD}
	\deproot[edge below, thick, edge style = {red}]{2}{W}
	\deproot[edge below, thick, edge style = {red}]{7}{WV}
	\deproot[edge below, thick, edge style = {red}]{10}{X}
	\depedge[edge below, thick, edge style = {red}]{6}{4}{E}
	\depedge[edge below, thick, edge style = {red}]{6}{5}{E}
  \end{dependency}

@@

\frame{\frametitle{Link Grammars}
Compare resulting dependency parse with CoNLL 2007 shared task. 
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\deproot[edge above, edge style = {blue, dotted}]{3}{\small ROOT}
	\depedge[edge below, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge above, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge above, edge style = {blue, dotted}]{3}{4}{\small ADV}
	\depedge[edge above, edge style = {blue, dotted}]{3}{5}{\small ADV}
	\depedge[edge below, edge style = {red, thick}]{3}{6}{I}
	\depedge[edge above, edge style = {blue, thick}]{3}{6}{\small VC}
	\depedge[edge above, edge style = {blue, dotted}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge below, edge style = {red, thick}]{2}{1}{D}
	\depedge[edge above, edge style = {blue, thick}]{2}{1}{\small NMOD}
	\depedge[edge below, edge style = {red, thick}]{7}{8}{MV}
	\depedge[edge above, edge style = {blue, thick}]{7}{8}{\small ADV}
	\depedge[edge below, edge style = {orange, thick}]{6}{7}{P}
	\depedge[edge above, edge style = {blue, thick}]{6}{7}{\small VC}
	\depedge[edge below, edge style = {red, thick}]{8}{9}{J}
	\depedge[edge above, edge style = {blue, thick}]{8}{9}{\small PMOD}
	\deproot[edge below, edge style = {red, dotted}]{2}{W}
	\deproot[edge below, edge style = {orange, ultra thick, dotted}]{7}{WV}
	\deproot[edge below, edge style = {red, dotted}]{10}{X}
	\depedge[edge below, edge style = {red, dotted}]{6}{4}{E}
	\depedge[edge below, edge style = {red, dotted}]{6}{5}{E}
  \end{dependency}

@@

\frame{\frametitle{Link Results: Subject-Verb links are backwards}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\deproot[edge above, edge style = {blue, dotted}]{3}{\small ROOT}
	\depedge[edge below, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge above, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge above, edge style = {blue, dotted}]{3}{4}{\small ADV}
	\depedge[edge above, edge style = {blue, dotted}]{3}{5}{\small ADV}
	\depedge[edge below, edge style = {red, thick}]{3}{6}{I}
	\depedge[edge above, edge style = {blue, thick}]{3}{6}{\small VC}
	\depedge[edge above, edge style = {blue, dotted}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge below, edge style = {red, thick}]{2}{1}{D}
	\depedge[edge above, edge style = {blue, thick}]{2}{1}{\small NMOD}
	\depedge[edge below, edge style = {red, thick}]{7}{8}{MV}
	\depedge[edge above, edge style = {blue, thick}]{7}{8}{\small ADV}
	\depedge[edge below, edge style = {orange, thick}]{6}{7}{P}
	\depedge[edge above, edge style = {blue, thick}]{6}{7}{\small VC}
	\depedge[edge below, edge style = {red, thick}]{8}{9}{J}
	\depedge[edge above, edge style = {blue, thick}]{8}{9}{\small PMOD}
	\deproot[edge below, edge style = {red, dotted}]{2}{W}
	\deproot[edge below, edge style = {orange, ultra thick, dotted}]{7}{WV}
	\deproot[edge below, edge style = {red, dotted}]{10}{X}
	\depedge[edge below, edge style = {red, dotted}]{6}{4}{E}
	\depedge[edge below, edge style = {red, dotted}]{6}{5}{E}
  \end{dependency}
\end{figure}

\begin{itemize}
\item[] %This is probably due to an inconsistency of the Link Grammar, discovered by our method.
\end{itemize}

@@

\frame{\frametitle{Link Results: Subject-Verb links are backwards}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\deproot[edge above, edge style = {gray}, hide label]{3}{\small ROOT}
	\depedge[edge below, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge above, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge above, edge style = {gray}, hide label]{3}{4}{\small ADV}
	\depedge[edge above, edge style = {gray}, hide label]{3}{5}{\small ADV}
	\depedge[edge below, edge style = {gray}, hide label]{3}{6}{I}
	\depedge[edge above, edge style = {gray}, hide label]{3}{6}{\small VC}
	\depedge[edge above, , edge style = {gray}, hide label, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge below, edge style = {gray}, hide label]{2}{1}{D}
	\depedge[edge above, edge style = {gray}, hide label]{2}{1}{\small NMOD}
	\depedge[edge below, edge style = {gray}, hide label]{7}{8}{MV}
    \depedge[edge above, edge style = {gray}, hide label]{7}{8}{\small ADV}
	\depedge[edge below, edge style = {gray}, hide label]{6}{7}{P}
	\depedge[edge above, edge style = {gray}, hide label]{6}{7}{\small VC}
	\depedge[edge below, edge style = {gray}, hide label]{8}{9}{J}
	\depedge[edge above, edge style = {gray}, hide label]{8}{9}{\small PMOD}
	\deproot[edge below, edge style = {gray}, hide label]{2}{W}
    \deproot[edge below, edge style = {gray}, hide label]{7}{WV}
	\deproot[edge below, edge style = {gray}, hide label]{10}{X}
	\depedge[edge below, edge style = {gray}, hide label]{6}{4}{E}
	\depedge[edge below, edge style = {gray}, hide label]{6}{5}{E}
  \end{dependency}
\end{figure}

@@

>>>>

%\setbeamerfont{page number in head/foot}{}
%\setbeamertemplate{footline}[frame number]

@@

\section{Motivation}

%\subsection{Multi-headed}
\frame{\frametitle{Multi-headedness}
  Multi-headedness Can Capture Additional Linguistic Phenomenon
  \begin{itemize}
    \item Control
    \item Relativization
    \item Conjunction
  \end{itemize}
}

@@

\subsection{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item[]  
    \item[]  
    \item[]  
  \end{itemize}
}

@@

\frame{\frametitle{Link Grammars: Example Parse}
\begin{figure}
  \begin{dependency}[edge style={-}]
	\begin{deptext}
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	\end{deptext}
	\depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	\depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	\depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	\depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	\depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	\deproot[edge above, thick, edge style = {red}]{2}{W}
	\deproot[edge above, thick, edge style = {red}]{7}{WV}
	\deproot[edge above, thick, edge style = {red}]{10}{X}
	\depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	\depedge[edge above, thick, edge style = {red}]{6}{5}{E}
  \end{dependency}
  \caption*{Link Parse of a sentence from Penn Tree Bank}
\end{figure}

@@

\frame{\frametitle{Link Grammars: Converting into a Directed Acyclic Graph}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	\end{deptext}
	\depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	\depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	\depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	\depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	\depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	\deproot[edge above, thick, edge style = {red}]{2}{W}
	\deproot[edge above, thick, edge style = {red}]{7}{WV}
	\deproot[edge above, thick, edge style = {red}]{10}{X}
	\depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	\depedge[edge above, thick, edge style = {red}]{6}{5}{E}
  \end{dependency}

@@

\frame{\frametitle{Link Grammars}
Compare resulting dependency parse with CoNLL 2007 shared task. 
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	\end{deptext}
	\deproot[edge below, thick, edge style = {blue}]{3}{\small ROOT}
	\depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	\depedge[edge below, thick, edge style = {blue}]{3}{2}{\small SBJ}
	\depedge[edge below, thick, edge style = {blue}]{3}{4}{\small ADV}
	\depedge[edge below, thick, edge style = {blue}]{3}{5}{\small ADV}
	\depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	\depedge[edge below, thick, edge style = {blue}]{3}{6}{\small VC}
	\depedge[edge below, thick, edge style = {blue}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	\depedge[edge below, thick, edge style = {blue}]{2}{1}{\small NMOD}
	\depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	\depedge[edge below, thick, edge style = {blue}]{7}{8}{\small ADV}
	\depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	\depedge[edge below, thick, edge style = {blue}]{6}{7}{\small VC}
	\depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	\depedge[edge below, thick, edge style = {blue}]{8}{9}{\small PMOD}
	\deproot[edge above, thick, edge style = {red}]{2}{W}
	\deproot[edge above, thick, edge style = {red}]{7}{WV}
	\deproot[edge above, thick, edge style = {red}]{10}{X}
	\depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	\depedge[edge above, thick, edge style = {red}]{6}{5}{E}
  \end{dependency}

@@

\frame{\frametitle{Link Grammars}
Compare resulting dependency parse with CoNLL 2007 shared task. 
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	\end{deptext}
	\deproot[edge below, edge style = {blue, dotted}]{3}{\small ROOT}
	\depedge[edge above, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge below, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge below, edge style = {blue, dotted}]{3}{4}{\small ADV}
	\depedge[edge below, edge style = {blue, dotted}]{3}{5}{\small ADV}
	\depedge[edge above, edge style = {red, thick}]{3}{6}{I}
	\depedge[edge below, edge style = {blue, thick}]{3}{6}{\small VC}
	\depedge[edge below, edge style = {blue, dotted}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge above, edge style = {red, thick}]{2}{1}{D}
	\depedge[edge below, edge style = {blue, thick}]{2}{1}{\small NMOD}
	\depedge[edge above, edge style = {red, thick}]{7}{8}{MV}
	\depedge[edge below, edge style = {blue, thick}]{7}{8}{\small ADV}
	\depedge[edge above, edge style = {orange, thick}]{6}{7}{P}
	\depedge[edge below, edge style = {blue, thick}]{6}{7}{\small VC}
	\depedge[edge above, edge style = {red, thick}]{8}{9}{J}
	\depedge[edge below, edge style = {blue, thick}]{8}{9}{\small PMOD}
	\deproot[edge above, edge style = {red, dotted}]{2}{W}
	\deproot[edge above, edge style = {orange, ultra thick, dotted}]{7}{WV}
	\deproot[edge above, edge style = {red, dotted}]{10}{X}
	\depedge[edge above, edge style = {red, dotted}]{6}{4}{E}
	\depedge[edge above, edge style = {red, dotted}]{6}{5}{E}
  \end{dependency}

@@

\frame{\frametitle{Link Results: Subject-Verb links are backwards}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	\end{deptext}
	\deproot[edge below, edge style = {blue, dotted}]{3}{\small ROOT}
	\depedge[edge above, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge below, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge below, edge style = {blue, dotted}]{3}{4}{\small ADV}
	\depedge[edge below, edge style = {blue, dotted}]{3}{5}{\small ADV}
	\depedge[edge above, edge style = {red, thick}]{3}{6}{I}
	\depedge[edge below, edge style = {blue, thick}]{3}{6}{\small VC}
	\depedge[edge below, edge style = {blue, dotted}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge above, edge style = {red, thick}]{2}{1}{D}
	\depedge[edge below, edge style = {blue, thick}]{2}{1}{\small NMOD}
	\depedge[edge above, edge style = {red, thick}]{7}{8}{MV}
	\depedge[edge below, edge style = {blue, thick}]{7}{8}{\small ADV}
	\depedge[edge above, edge style = {orange, thick}]{6}{7}{P}
	\depedge[edge below, edge style = {blue, thick}]{6}{7}{\small VC}
	\depedge[edge above, edge style = {red, thick}]{8}{9}{J}
	\depedge[edge below, edge style = {blue, thick}]{8}{9}{\small PMOD}
	\deproot[edge above, edge style = {red, dotted}]{2}{W}
	\deproot[edge above, edge style = {orange, ultra thick, dotted}]{7}{WV}
	\deproot[edge above, edge style = {red, dotted}]{10}{X}
	\depedge[edge above, edge style = {red, dotted}]{6}{4}{E}
	\depedge[edge above, edge style = {red, dotted}]{6}{5}{E}
  \end{dependency}
\end{figure}

@@

\frame{\frametitle{Link Results: Subject-Verb links are backwards}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	\end{deptext}
	\deproot[edge below, edge style = {gray}, hide label]{3}{\small ROOT}
	\depedge[edge above, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge below, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge below, edge style = {gray}, hide label]{3}{4}{\small ADV}
	\depedge[edge below, edge style = {gray}, hide label]{3}{5}{\small ADV}
	\depedge[edge above, edge style = {gray}, hide label]{3}{6}{I}
	\depedge[edge below, edge style = {gray}, hide label]{3}{6}{\small VC}
	\depedge[edge below, , edge style = {gray}, hide label, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge above, edge style = {gray}, hide label]{2}{1}{D}
	\depedge[edge below, edge style = {gray}, hide label]{2}{1}{\small NMOD}
	\depedge[edge above, edge style = {gray}, hide label]{7}{8}{MV}
    \depedge[edge below, edge style = {gray}, hide label]{7}{8}{\small ADV}
	\depedge[edge above, edge style = {gray}, hide label]{6}{7}{P}
	\depedge[edge below, edge style = {gray}, hide label]{6}{7}{\small VC}
	\depedge[edge above, edge style = {gray}, hide label]{8}{9}{J}
	\depedge[edge below, edge style = {gray}, hide label]{8}{9}{\small PMOD}
	\deproot[edge above, edge style = {gray}, hide label]{2}{W}
    \deproot[edge above, edge style = {gray}, hide label]{7}{WV}
	\deproot[edge above, edge style = {gray}, hide label]{10}{X}
	\depedge[edge above, edge style = {gray}, hide label]{6}{4}{E}
	\depedge[edge above, edge style = {gray}, hide label]{6}{5}{E}
  \end{dependency}
\end{figure}

\frame{\frametitle{Link Results: Subject-Verb links are backwards}

@@

\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  Jill \& wanted \& to \& skip \\
	\end{deptext}
    \deproot[edge above, edge unit distance=2ex]{1}{W}
    \deproot[edge above, edge unit distance=2ex]{2}{WV}
	\depedge[edge above]{2}{1}{S}
	\depedge[edge above]{2}{3}{TO}
	\depedge[edge above]{3}{4}{I}
	\depedge[edge above]{2}{4}{IV}
  \end{dependency}
\end{figure}

\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  Jill \& persuaded \& him \& to \& skip \\
	\end{deptext}
    \deproot[edge above, edge unit distance=2ex]{1}{W}
    \deproot[edge above, edge unit distance=2ex]{2}{WV}
	\depedge[edge above]{2}{1}{S}
	\depedge[edge above]{2}{3}{O}
	\depedge[edge above]{2}{4}{TO}
	\depedge[edge above]{4}{5}{I}
	\depedge[edge above]{2}{5}{IV}
  \end{dependency}
\end{figure}
